### 2024-06-05 thesis/input_files/point.tex
cleaned all problems and warnings
final thesis

\subsection{Autoregressive integrated moving average with exogenous variables}
The ARIMAX model adds explanatory variables to ARIMA. Hence, we have
\begin{equation}
    \hat{y}_n=\sum\limits_{k=1}^{h} \mu_i X_{n-k}+\sum\limits_{i=1}^{p}\psi_i y_{n-i}^{(d)}+\sum\limits_{j=1}^{q}\theta_j \epsilon_{n-j}+ \epsilon_{n}
\end{equation}
\subsection{Seasonal autoregressive integrated moving average and seasonal autoregressive integrated moving average with exogenous variables}
SARIMA and SARIMAX incorporate seasonalities into time series models. The notation for these models is ARIMA$(p,d,q)(P,D,Q)_m$. The second term $(P,D,Q)_m$ represents the autoregressive structure of the seasonal pattern, where $m$ indicates the number of seasonalities of the time series.
For instance, in modelling series of hourly data with daily periodicity, we would set $m=24$.
Writing SARIMA in compact notation we have
\\
\begin{equation}
    \psi(B)\Psi(B^P)\nabla^d\nabla_m^Dy_t=\theta(B)\Theta(B^Q)\epsilon_t
\end{equation}
where $\Psi$ and $\Theta$ account for the $P$ and $Q$ of the seasonal pattern $m$ respectively.
\section{Generalised additive model}
% in standard regression the predicted y are normal since error are normal. But if we want to model say a y bernoulli which is the rate of success we can link the domain of bernoulli to that of gaussian with a link function
Generalised additive models (GAMs) take the form
\begin{equation}
    g[\mathbb{E}(Y_i)]=\alpha+f_1(X_1)+\dots+f_p(X_p)
\end{equation}
$f_i$ are smooth functions which are fitted using cubic smoothing splines.
Herein, $g$ is called link function and characterizes the specific GAM model \cite{hastie2017generalized}. Approximations for $f_i$ are obtained through an iterative procedure, the backfitting algorithm.

@@

Smola et al.\ \cite{smola2004tutorial} point out that considering the dual formulation makes our optimisation problem easier to solve. Doing so, we have the equivalent optimisation problem

@@

% https://rtavenar.github.io/deep_book/book_en.pdf
Long short term memory network (LSTM) extends MLP by introducing a cell state in its layers \cite{hochreiter1997long}. In this way, the current state of a cell depends on the current value $X_t$, on the previous cell activation and on the previous cell state $C_{t-1}$, see Figure \ref{fig:lstm_cell} for a visual representation. 
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/lstm_cell.png}
    \caption{Long short term memory cell \cite{Han2024}}
    \label{fig:lstm_cell}
\end{figure}
The cell is responsible for deciding whether to store/forget long and short term information. To do so, each cell is made of a forget gate, an input gate and an output gate.
The forget gate takes in $h_{t-1}$ and $x_t$ and outputs a real valued vector with elements in $[0,1]$. This corresponds to the ratio of information retention for each element of the cell state $C_{t-1}$.
\\
Its equation is given by
\begin{equation}
    f_t=\sigma(W_f[h_{t-1},x_t]+b_f)
\end{equation}
The input gate is made up of two parts. First, a sigmoid layer decides which values of the cell state will be updated. Second, a tanh layer creates a vector of candidates $\tilde{C}_t$ to add to the current state.
\begin{equation}
    \begin{aligned}
        i_t=&\sigma(W_i [h_{t-1},x_t]+b_i)
        \\
        \tilde{C}_t=&tanh(W_C [h_{t-1},x_t]+b_C)
    \end{aligned}
\end{equation}
The cell state is then updated by
\begin{equation}
    C_t=f_t\odot C_{t-1}+i_t\odot \tilde{C}_t
    % odot is elementwise product
\end{equation}
Finally, we output the current cell state and the tanh activated cell state filtered by the sigmoid layer on the current input and the previous hidden state.
\begin{equation}
    \begin{aligned}
    o_t=& \sigma(W_o[h_{t-1},x_t]+b_o)
    \\
    h_t=& o_t \odot tanh(C_t)
\end{aligned}
\end{equation}
% \subsection{DeepAr} deepar é probabilistic

@@

\section{Kernel methods}
\subsection{Kernel ridge regression}
In the setting of kernel ridge regression, we aim at estimating $f$ such that $y=f(x)+\epsilon$. Given an RKHS $\mathcal{H}$, we can estimate $f$ by solving the optmisation problem
\begin{equation}\label{eq:kernel ridge}
    \hat{f}=\argmin{f\in \mathcal{H}}\frac{1}{2}\sum\limits_{i=1}^n(y_i-f(x_i))^2+\frac{\tau}{2}\|f\|_{\mathcal{H}}^2
\end{equation}
Before proceeding, we need to introduce the representer theorem.
\begin{theorem}
    Let $k:\mathcal{X} \times \mathcal{X} \to \mathbb{R}$ on a non empty set $\mathcal{X}$ with corresponding RKHS $\mathcal{H}$,
    a strictly increasing real valued function $g:[0,\infty) \to \mathbb{R}$, and the loss function $E:(\mathcal{X}\times \mathbb{R}^2)^n \to \mathbb{R} \cup \{\infty\}$.
    Consider the regularised risk functional $Risk[f]:f \mapsto  E\left((x_{1},y_{1},f(x_{1})),\ldots, (x_{n},y_{n},f(x_{n}))\right)+g\left(\| f\|_{\mathcal{H}} \right)$. Then any minimiser of the empirical risk can be represented as $$ f^{*}(\cdot )=\sum\limits_{i=1}^{n}\alpha _{i}k(\cdot ,x_{i})$$
\end{theorem}

@@

\subsection{Kernel support vector regression}
Support vector regression (SVR) can be kernelized by swapping the $\mathbb{R}^n$ Euclidean inner product of $x$ with the inner product in the higher feature space $\mathcal{H}$. Doing so, the optimisation problem can be restated as
\begin{equation}
    \begin{aligned}
        \max_{\lambda_i, \lambda_i^*} \quad& -\frac{1}{2}\sum\limits_{i,j=1}^n(\lambda_i-\lambda_i^*)(\lambda_i-\lambda_i^*)k(x_i, x_j)+\sum\limits_{i=1}^n(y_i-\epsilon)(\lambda_i-\lambda_i^*)
        \\
        s.t. \quad& \sum\limits_{i=1}^n(\lambda_i-\lambda_i^*)=0
        \\
        \quad& \lambda_i, \lambda_i^* \in [0,C]
    \end{aligned}
\end{equation}
Letting $\alpha_i=\lambda_i - \lambda_i^*$, our regressor $f$ is then given by
\begin{equation}
    \begin{aligned}
        f(x)=\sum\limits_{i=1}^n \alpha_i k(x_i, x)+b
    \end{aligned}
\end{equation}
Notice, in this setting $w$ is no longer given explicitly. Additionally, with kernel support vector regression we seek for the flattest function in the feature space instead of the input space.
See Figure \ref{fig:svr2} and Figure \ref{fig:svr3} for two examples. In the former, we have used a polynomial kernel and the standard radial basis function kernel in the latter.
\begin{figure}
    \includegraphics[width=\textwidth]{images/svr2.png}
    \caption{Polynomial support vector regression}
    \label{fig:svr2}
\end{figure}

\begin{figure}
    \includegraphics[width=\textwidth]{images/svr3.png}
    \caption{Gaussian RBF support vector regression}
    \label{fig:svr3}
\end{figure}
Comparing these pictures with Figure \ref{fig:svr1}, it can be concluded that introducing kernels allows support vector regression to handle non linearities in the data.

>>>>

\subsection{Autoregressive integrated moving average with exogenous variables}
The ARIMAX model adds explanatory variables to ARIMA. Hence, we have
\begin{equation}
    \hat{y}_n=\sum\limits_{k=1}^{h} \mu_i X_{n-k}+\sum\limits_{i=1}^{p}\psi_i y_{n-i}^{(d)}+\sum\limits_{j=1}^{q}\theta_j \epsilon_{n-j}+ \epsilon_{n}
\end{equation}
\subsection{Seasonal autoregressive integrated moving average and seasonal autoregressive integrated moving average with exogenous variables}
SARIMA and SARIMAX incorporate seasonalities into time series models. The notation for these models is ARIMA$(p,d,q)(P,D,Q)_m$. The second term $(P,D,Q)_m$ represents the autoregressive structure of the seasonal pattern, where $m$ indicates the number of seasonalities of the time series.
For instance, in modelling series of hourly data with daily periodicity, we would set $m=24$.
Writing SARIMA in compact notation we have

\begin{equation}
    \psi(B)\Psi(B^P)\nabla^d\nabla_m^Dy_t=\theta(B)\Theta(B^Q)\epsilon_t
\end{equation}
where $\Psi$ and $\Theta$ account for the $P$ and $Q$ of the seasonal pattern $m$ respectively.
\section{Generalised additive model}
% in standard regression the predicted y are normal since error are normal. But if we want to model say a y bernoulli which is the rate of success we can link the domain of bernoulli to that of gaussian with a link function
Generalised additive models (GAMs) take the form
\begin{equation}
    g[\mathbb{E}(Y_i)]=\alpha+f_1(X_1)+\dots+f_p(X_p)
\end{equation}
$f_i$ are smooth functions which are fitted using cubic smoothing splines.
Herein, $g$ is called link function and characterizes the specific GAM model \cite{hastie2017generalized}. Approximations for $f_i$ are obtained through an iterative procedure, the backfitting algorithm.

@@

Smola et al.\ \cite{smola2004tutorial} points out that considering the dual formulation makes our optimisation problem easier to solve. Doing so, we have the equivalent optimisation problem

@@

% https://rtavenar.github.io/deep_book/book_en.pdf
Long short term memory network (LSTM) extends MLP by introducing a cell state in its layers \cite{hochreiter1997long}. In this way, the current state of a cell depends on the current value $X_t$, on the previous cell activation and on the previous cell state $C_{t-1}$, see Figure \ref{fig:lstm_cell} for a visual representation. 
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{images/lstm_cell.png}
    \caption{Long short term memory cell \cite{Han2024}}
    \label{fig:lstm_cell}
\end{figure}
The cell is responsible for deciding whether to store/forget long and short term information. To do so, each cell is made of a forget gate, an input gate and an output gate.
The forget gate takes in $h_{t-1}$ and $x_t$ and outputs a real valued vector with elements in $[0,1]$. This corresponds to the ratio of information retention for each element of the cell state $C_{t-1}$.
\\
Its equation is given by
\begin{equation}
    f_t=\sigma(W_f[h_{t-1},x_t]+b_f)
\end{equation}
The input gate is made up of two parts. First, a sigmoid layer decides which values of the cell state will be updated. Second, a tanh layer creates a vector of candidates $\tilde{C}_t$ to add to the current state.
\begin{equation}
    \begin{aligned}
        i_t=&\sigma(W_i [h_{t-1},x_t]+b_i)
        \\
        \tilde{C}_t=&tanh(W_C [h_{t-1},x_t]+b_C)
    \end{aligned}
\end{equation}
The cell state is then updated by
\begin{equation}
    C_t=f_t\odot C_{t-1}+i_t\odot \tilde{C}_t
    % odot is elementwise product
\end{equation}
Finally, we output the current cell state and the tanh activated cell state filtered by the sigmoid layer on the current input and the previous hidden state.
\begin{equation}
    \begin{aligned}
    o_t=& \sigma(W_o[h_{t-1},x_t]+b_o)
    \\
    h_t=& o_t \odot tanh(C_t)
\end{aligned}
\end{equation}
% \subsection{DeepAr} deepar é probabilistic

@@

\section{Kernel methods}
\subsection{Kernel ridge regression}
In the setting of kernel ridge regression, we aim at estimating $f$ such that $y=f(x)+\epsilon$. Given a RKHS $\mathcal{H}$, we can estimate $f$ by solving the optmisation problem
\begin{equation}\label{eq:kernel ridge}
    \hat{f}=\argmin{f\in \mathcal{H}}\frac{1}{2}\sum\limits_{i=1}^n(y_i-f(x_i))^2+\frac{\tau}{2}\|f\|_{\mathcal{H}}^2
\end{equation}
Before proceeding, we need to introduce the representer theorem.
\begin{theorem}
    Let $k:\mathcal{X} \times \mathcal{X} \to \mathbb{R}$ on a non empty set $\mathcal{X}$ with corresponding RKHS $\mathcal{H}$,
    a strictly increasing real valued function $g:[0,\infty) \to \mathbb{R}$, and the loss function $E:(\mathcal{X}\times \mathbb{R}^2)^n \to \mathbb{R} \cup \{\infty\}$.
    Consider the regularised risk functional $Risk[f]:f \mapsto  E\left((x_{1},y_{1},f(x_{1})),\ldots, (x_{n},y_{n},f(x_{n}))\right)+g\left(\| f\|_{\mathcal{H}} \right)$. Then any minimiser of the empirical risk can be represented as $$ f^{*}(\cdot )=\sum\limits_{i=1}^{n}\alpha _{i}k(\cdot ,x_{i})$$
\end{theorem}

@@

\subsection{Kernel support vector regression}
Support vector regression (SVR) can be kernelized by swapping the $\mathbb{R}^n$ Euclidean inner product of $x$ with the inner product in the higher feature space $\mathcal{H}$. Doing so, the optimisation problem can be restated as
\begin{equation}
    \begin{aligned}
        \max_{\lambda_i, \lambda_i^*} \quad& -\frac{1}{2}\sum\limits_{i,j=1}^n(\lambda_i-\lambda_i^*)(\lambda_i-\lambda_i^*)k(x_i, x_j)+\sum\limits_{i=1}^n(y_i-\epsilon)(\lambda_i-\lambda_i^*)
        \\
        s.t. \quad& \sum\limits_{i=1}^n(\lambda_i-\lambda_i^*)=0
        \\
        \quad& \lambda_i, \lambda_i^* \in [0,C]
    \end{aligned}
\end{equation}
Letting $\alpha_i=\lambda_i - \lambda_i^*$, our regressor $f$ is then given by
\begin{equation}
    \begin{aligned}
        f(x)=\sum\limits_{i=1}^n \alpha_i k(x_i, x)+b
    \end{aligned}
\end{equation}
Notice, in this setting $w$ is no longer given explicitly. Additionally, with kernel support vector regression we seek for the flattest function in the feature space instead of the input space.
See Figure \ref{fig:svr2} and Figure \ref{fig:svr3} for two examples. In the former, we have used a polynomial kernel and the standard radial basis function kernel in the latter.
\begin{figure}
    \includegraphics[width=\textwidth]{images/svr2.png}
    \caption{Polynomial support vector regression}
    \label{fig:svr2}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{images/svr3.png}
    \caption{Gaussian RBF support vector regression}
    \label{fig:svr3}
\end{figure}
Comparing these pictures with Figure \ref{fig:svr1}, it can be concluded that introducing kernels allows support vector regression to handle non linearities in the data.

### 2024-06-05 thesis/input_files/probabilistic.tex
cleaned all problems and warnings
final thesis

Suppose now to partition the feature space into M regions $R_1,\dots,R_M$, then the model reads as follows.
\begin{equation}
    f(x)=\sum\limits_{m=1}^{M}c_m\mathbb{I}_{\{x \in R_m\}}
\end{equation}

@@

% \section{Kernel methods}
\section{Kernel quantile regression}
The idea of quantile regression has been extended to kernel methods by Takeuchi et al.\ \cite{takeuchi2006nonparametric}.
There, they minimise a risk functional plus regulariser defined as follows.
\begin{equation}\label{eq:kqr_min1}
    Risk[f]:=\frac{1}{m}\sum\limits_{i=1}^{m}\rho_q(y_i-f(x_i))+\frac{\tau}{2}\|w\|_\mathcal{H}^2
\end{equation}
where $f=w+b$, $w \in \mathcal{H}$ and $b \in \mathbb{R}$.
Using the link between RKHS and feature spaces, we can rewrite $f(x)=\langle w, \phi(x) \rangle_{\mathcal{H}}+b$. 
% Moreover, note that the RKHS norm is defined as follows $\|f\|_{\mathcal{H}}=\inf\{\|w\|_{\mathcal{F}}:w\in \mathcal{F},f(x)=\langle w,\varphi (x)\rangle _{\mathcal{F}},\forall x\in X\}$, where $\mathcal{F}$ is the feature space.
 Doing so we obtain a minimisation problem equivalent to minimising equation \ref{eq:kqr_min1}.
\begin{equation}\label{eq:kqr_min2}
    \begin{split}
        \min_{w,b} \quad & C \sum \limits_{i=1}^{m} \hbox{$q(y_i - \langle w, \phi(x_i) \rangle_{\mathcal{H}} - b)$} \\
        & + \hbox{$(1-q)(-y_i + \langle w, \phi(x_i) \rangle_{\mathcal{H}} + b)$} \\
        & + \frac{1}{2}\|w\|_{\mathcal{H}}^2
    \end{split}
    \end{equation}
Note the division by $\tau$ so that $C:=\frac{1}{\tau m}$.
\\
We can next rephrase the optimisation in Equation \ref{eq:kqr_min2} by introducing the slack variables $\xi_i$ and $\xi_i^*$.
\begin{equation}\label{eq:kqr_min3}
    \begin{aligned}
        \min_{w,b,\xi_i,\xi_i^*} \quad & C \sum \limits_{i=1}^{m}
        q \xi_i+ (1-q)\xi_i^*+ \frac{1}{2}\|w\|_{\mathcal{H}}^2\\
    \textrm{s.t.} \quad & y_i-\langle w, \phi(x_i) \rangle_{\mathcal{H}}-b \leq \xi_i\\
    & -y_i+\langle w, \phi(x_i) \rangle_{\mathcal{H}}+b \leq \xi_i^*\\
      &\xi_i\geq0    \\
      &\xi_i^*\geq0    \\
    \end{aligned}
    \end{equation}
In order to make it more compact, we rewrite Equation \ref{eq:kqr_min3} in matrix notation.
\begin{equation}\label{eq:kqr_min4}
    \begin{aligned}
        \min_{w,b\xi,\xi^*} \quad & C q \xi^\intercal \mathbb{1}+ C (1-q) (\xi^*)^\intercal \mathbb{1}+ \frac{1}{2}w^\intercal w\\
    \textrm{s.t.} \quad & y-\Phi^\intercal w -b \preceq \xi\\
    & -y+\Phi^\intercal w +b \preceq \xi^*\\
      &\xi\succeq0    \\
      &\xi^*\succeq0    \\
    \end{aligned}
    \end{equation}
Consider now, the Lagrangian $\mathcal{L}$ associated to Equation \ref{eq:kqr_min4}
\begin{equation}\label{eq:kqr_min5}
    \begin{split}
        L(w, b, \xi, \xi^*) = \quad & \hbox{$C q \xi^\intercal \mathbb{1} + C (1-q) (\xi^*)^\intercal \mathbb{1} + \frac{1}{2} w^\intercal w$} \\
        & \hbox{$- \lambda^\intercal (\xi - y + \Phi^\intercal w + b)$} \\
        & \hbox{$- (\lambda^*)^\intercal (\xi^* + y - \Phi^\intercal w - b)$} \\
        & \hbox{$- \nu^\intercal \xi - (\nu^*)^\intercal \xi^*$}
    \end{split}
\end{equation}
The next step is deriving its dual formulation, since it is easier and more efficient to solve. This because the dual problem has the useful property of being always convex.

@@

First, take the dual function from Equation \ref{eq:kqr_min5}.
\begin{equation}
    \begin{aligned}
        g(\lambda, \lambda^*, \nu, \nu^*)= & \inf_{\xi, \xi^*, w, b} \mathcal{L}(w,b,\xi,\xi^*,\lambda, \lambda^*, \nu, \nu^*)
\end{aligned}
\end{equation}
Setting its derivatives to zero
\begin{equation}\label{eq:lagrange_derivatives}
    \begin{cases}
        \frac{\partial \mathcal{L}}{\partial w}=0 \implies w=\Phi^\intercal(\lambda-\lambda^*)
        \\
        \frac{\partial \mathcal{L}}{\partial b}=0 \implies (\lambda-\lambda^*)^\intercal\mathbb{1}=0
        \\
        \frac{\partial \mathcal{L}}{\partial \xi}=0 \implies Cq \mathbb{1}-\lambda- \nu=0
        \\
        \frac{\partial \mathcal{L}}{\partial \xi^*}=0 \implies C(1-q)\mathbb{1} -\lambda^* -\nu^*=0
    \end{cases}
\end{equation}
As pointed out previously, the lower bound resulting from the dual formulation is non trivial only when the Lagrange multipliers $\lambda$ are $\succeq 0$. Looking at the last two equations of the system \ref{eq:lagrange_derivatives}, this implies the following two constraints $\lambda \in [0, Cq\mathbb{1}]$ and $\lambda^*\in [0, C(1-q)\mathbb{1}]$.

@@

We conclude this chapter with reporting the same kind of Tables \ref{tab:kernel pinball comparison}, \ref{tab:kernel pinball comparison quantile-wise}, \ref{tab:kernel mae comparison} and Figures \ref{fig:kernel quantile regressors comparison1},\ref{fig:kernel quantile regressors comparison2} comparing various kernel functions, see Section \ref{kernel families}.
From these tables, we can conclude that the Matern and the Chi squared kernels are the top performers on the Melbourne weather data. Finally, the equality in the scores of the Absolute Laplacian and the Matern 0.5 follows from the fact that regressors are one dimensional for the Melbourne weather data.
% tables
\begin{table}[!htp]
    \caption{Kernels comparison pinball loss for Melbourne data}
    \label{tab:kernel pinball comparison}
    \begin{center}
    \begin{tabular}{lll}
        \toprule
        & Kernel & Pinball loss
        \\
        \midrule
        & Absolute Laplacian &  10.136551 \\
        & Matern 0.5/Laplacian & 10.136551  \\
        & Matern 1.5 & 10.082668  \\
        & Matern 2.5 & 10.0494190    \\

>>>>

Suppose now to partition the feature space into $M$ regions $R_1,\dots,R_M$, then the model reads as follows.
\begin{equation}
    f(x)=\sum\limits_{m=1}^{M}c_m\mathbb{I}_{\{x \in R_m\}}
\end{equation}

@@

% \section{Kernel methods}
\section{Kernel quantile regression}
The idea of quantile regression has been extended to kernel methods by Takeuchi et al.\ \cite{takeuchi2006nonparametric}.
There, they minimise a risk functional plus regulariser defined as follows.
\begin{equation}\label{eq:kqr_min1}
    Risk[f]:=\frac{1}{m}\sum\limits_{i=1}^{m}\rho_q(y_i-f(x_i))+\frac{\tau}{2}\|w\|_\mathcal{H}^2
\end{equation}
where $f=w+b$, $w \in \mathcal{H}$ and $b \in \mathbb{R}$.
Using the link between RKHS and feature spaces, we can rewrite $f(x)=\langle w, \phi(x) \rangle_{\mathcal{H}}+b$. 
% Moreover, note that the RKHS norm is defined as follows $\|f\|_{\mathcal{H}}=\inf\{\|w\|_{\mathcal{F}}:w\in \mathcal{F},f(x)=\langle w,\varphi (x)\rangle _{\mathcal{F}},\forall x\in X\}$, where $\mathcal{F}$ is the feature space.
 Doing so we obtain a minimisation problem equivalent to minimising equation \ref{eq:kqr_min1}.
\begin{equation}\label{eq:kqr_min2}
    \begin{split}
        \min_{w,b} \quad & C \sum \limits_{i=1}^{m} \hbox{$q(y_i - \langle w, \phi(x_i) \rangle_{\mathcal{H}} - b)$} \\
        & + \hbox{$(1-q)(-y_i + \langle w, \phi(x_i) \rangle_{\mathcal{H}} + b)$} \\
        & + \frac{1}{2}\|w\|_{\mathcal{H}}^2
    \end{split}
    \end{equation}
Note the division by $\tau$ so that $C:=\frac{1}{\tau m}$.
\\
We can next rephrase the optimisation in Equation \ref{eq:kqr_min2} by introducing the slack variables $\xi_i$ and $\xi_i^*$.
\begin{equation}\label{eq:kqr_min3}
    \begin{aligned}
        \min_{w,b,\xi_i,\xi_i^*} \quad & C \sum \limits_{i=1}^{m}
        q \xi_i+ (1-q)\xi_i^*+ \frac{1}{2}\|w\|_{\mathcal{H}}^2\\
    \textrm{s.t.} \quad & y_i-\langle w, \phi(x_i) \rangle_{\mathcal{H}}-b \leq \xi_i\\
    & -y_i+\langle w, \phi(x_i) \rangle_{\mathcal{H}}+b \leq \xi_i^*\\
      &\xi_i\geq0    \\
      &\xi_i^*\geq0    \\
    \end{aligned}
    \end{equation}
In order to make it more compact, we rewrite Equation \ref{eq:kqr_min3} in matrix notation.
\begin{equation}\label{eq:kqr_min4}
    \begin{aligned}
        \min_{w,b\xi,\xi^*} \quad & C q \xi^\intercal \mathbb{1}+ C (1-q) (\xi^*)^\intercal \mathbb{1}+ \frac{1}{2}w^\intercal w\\
    \textrm{s.t.} \quad & y-\Phi^\intercal w -b \preceq \xi\\
    & -y+\Phi^\intercal w +b \preceq \xi^*\\
      &\xi\succeq0    \\
      &\xi^*\succeq0    \\
    \end{aligned}
    \end{equation}
Consider now, the Lagrangian $\mathcal{L}$ associated to Equation \ref{eq:kqr_min4}
\begin{equation}\label{eq:kqr_min5}
    \begin{split}
        L(w, b, \xi, \xi^*) = \quad & \hbox{$C q \xi^\intercal \mathbb{1} + C (1-q) (\xi^*)^\intercal \mathbb{1} + \frac{1}{2} w^\intercal w$} \\
        & \hbox{$- \lambda^\intercal (\xi - y + \Phi^\intercal w + b)$} \\
        & \hbox{$- (\lambda^*)^\intercal (\xi^* + y - \Phi^\intercal w - b)$} \\
        & \hbox{$- \nu^\intercal \xi - (\nu^*)^\intercal \xi^*$}
    \end{split}
\end{equation}
The next step is deriving its dual formulation, since it is easier and more efficient to solve. This because the dual problem is always convex.

@@

First, take the dual function from Equation \ref{eq:kqr_min5}.
\begin{equation}
    \begin{aligned}
        g(\lambda, \lambda^*, \nu, \nu^*)= & \inf_{\xi, \xi^*, w, b} \mathcal{L}(w,b,\xi,\xi^*,\lambda, \lambda^*, \nu, \nu^*)
\end{aligned}
\end{equation}
Setting its derivatives to zero
\begin{equation}\label{eq:lagrange_derivatives}
    \begin{cases}
        \frac{\partial \mathcal{L}}{\partial w}=0 \implies w=\Phi^\intercal(\lambda-\lambda^*)
        \\
        \frac{\partial \mathcal{L}}{\partial b}=0 \implies (\lambda-\lambda^*)^\intercal\mathbb{1}=0
        \\
        \frac{\partial \mathcal{L}}{\partial \xi}=0 \implies Cq \mathbb{1}-\lambda- \nu=0
        \\
        \frac{\partial \mathcal{L}}{\partial \xi^*}=0 \implies C(1-q)\mathbb{1} -\lambda^* -\nu^*=0
    \end{cases}
\end{equation}
As pointed out previously, the lower bound resulting from the dual formulation is non trivial only when the Lagrange multipliers $\lambda$ are $\succeq 0$. Looking at the last two equations of the System \ref{eq:lagrange_derivatives}, this implies the following two constraints $\lambda \in [0, Cq\mathbb{1}]$ and $\lambda^*\in [0, C(1-q)\mathbb{1}]$.

@@

We conclude this chapter with reporting the same kind of Tables \ref{tab:kernel pinball comparison}, \ref{tab:kernel pinball comparison quantile-wise}, \ref{tab:kernel mae comparison} and Figures \ref{fig:kernel quantile regressors comparison1}, \ref{fig:kernel quantile regressors comparison2} comparing various kernel functions, see Section \ref{kernel families}.
From these tables, we can conclude that the Matern and the Chi squared kernels are the top performers on the Melbourne weather data. Finally, the equality in the scores of the Absolute Laplacian and the Matern 0.5 follows from the fact that regressors are one dimensional for the Melbourne weather data.
% tables
\begin{table}[!htp]
    \caption{Kernels comparison pinball loss for Melbourne data}
    \label{tab:kernel pinball comparison}
    \begin{center}
    \begin{tabular}{lll}
        \toprule
        & Kernel & Pinball loss
        \\
        \midrule
        & Absolute Laplacian &  10.136551 \\
        & Matern 0.5/Laplacian & 10.136551  \\
        & Matern 1.5 & 10.082668  \\
        & Matern 2.5 & 10.0494190    \\
